### 2014-06-04 Equipment/Equipment_Guide/Equipment_Guide.tex
Update equipment guide

\section{Software}
Channel lists are built using NI-MAX and fed into 32-bit NI LabVIEW as a task using DAQ-mX. Note that in the current configuration, the laptop must also have a 32-bit operating system on it.

@@

Two different welders are used to construct the bare bead TCs.

>>>>

\section{Software}
Channel lists are built using NI-MAX and fed into 32-bit NI LabVIEW as a task using DAQ-mX. Note that in the current configuration, the computer must also have a 32-bit operating system on it.

@@

Two different welders are used to construct the bare bead TCs. The Miyachi Unitek TC Welder (01-0196-02) is a manual feed thermocouple welder designed to weld thermocouple wires together without oxide layers by using argon cover gas. The welder can handle wires from 38 gauge to 20 gauge.
